# Tables are fun

```{r message=FALSE, warning=FALSE}
library(tidyverse)
# library(gt)
```


Tables can be a challenge to render

https://bookdown.org/yihui/bookdown/tables.html

## Paged tables are interactive but only work in .nb.html

```{r}
starwars
```


## non-interactive

Old school, BUT easily cross functional with PDF and HTML alike

```{r tidy=FALSE}
knitr::kable(
  head(starwars %>% select(1:6), 8), caption = 'Another nice table!',
  booktabs = TRUE
)
```

## Great Tables

the [`gt` package](https://gt.rstudio.com/) is awesome but doesn't work in PDF.  Additionally, the `knitr::kable()` function has some organizatonal and referencing features that you may prefer to have handled automatically.  

Until `gt` moves beyond the development you may want to avoid this approach.

```{r eval=FALSE}
starwars %>% 
  select(1:4) %>% 
  slice_head(n = 8) %>% 
  gt() %>% 
  tab_header(
    title = md("**_Star Wars_ characters**"),
    subtitle = "subtitles are cool"
    ) %>% 
  tab_source_note(
    source_note = md("Source:  `dplyr::starwars`")
    ) %>% 
  tab_options(heading.background.color = "darkseagreen") 
```



None of this was based on a book by John Little [@Little2018].


## Math Expressions

You can make Inline LaTeX equations

$$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$$

The above is done with   `$$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$$`

[Recommendation to R Markdown syntax unless](https://bookdown.org/yihui/rmarkdown/rticles-latex.html) there are specific requirements for using LaTeX.  

Read more about [Markdown syntax for Math expressions](https://bookdown.org/yihui/bookdown/markdown-syntax.html#math-expressions)
